---
title: "48bhw1"
output: html_document
---

```{r setup, include=FALSE}

library(readr)
library(scatterplot3d)
library(repr)
library(rgl)
library(pracma)
library(reshape2)
library(data.table)
library(ggplot2)
library(TSrepr)
library(rpart)
library(zoo)
library(rattle)

x_acc <- read_table("D:/İndirilenler/uWaveGestureLibrary_X_TRAIN",col_names = FALSE)
y_acc <- read_table("D:/İndirilenler/uWaveGestureLibrary_Y_TRAIN",col_names = FALSE)
z_acc <- read_table("D:/İndirilenler/uWaveGestureLibrary_Z_TRAIN",col_names = FALSE)

x_move=as.vector(x_acc[92,])
z_move=as.vector(z_acc[92,])
y_move=as.vector(y_acc[92,])

total <- rbind(x_move,y_move,z_move)
total=t(total)
total=total[-1,]
total=as.data.frame(total)
names(total)=c('x_acc','y_acc','z_acc')




acceleration=as.ts(total)




velocity_x=cumsum(total$x_acc)
velocity_y=cumsum(total$y_acc)
velocity_z=cumsum(total$z_acc)

velocity=data.frame(velocity_x,velocity_y,velocity_z)
tsvelocity=as.ts(velocity)


location_x=cumsum(velocity_x)
location_y=cumsum(velocity_y)
location_z=cumsum(velocity_z)
location=data.frame(location_x,location_y,location_z)
tslocation=as.ts(location)

location8=location

x_move=as.vector(x_acc[128,])
z_move=as.vector(z_acc[128,])
y_move=as.vector(y_acc[128,])


total <- rbind(x_move,y_move,z_move)
total=t(total)
total=total[-1,]
total=as.data.frame(total)
names(total)=c('x_acc','y_acc','z_acc')

velocity_x=cumsum(total$x_acc)
velocity_y=cumsum(total$y_acc)
velocity_z=cumsum(total$z_acc)
velocity=data.frame(velocity_x,velocity_y,velocity_z)


location_x=cumsum(velocity_x)
location_y=cumsum(velocity_y)
location_z=cumsum(velocity_z)
location=data.frame(location_x,location_y,location_z)

location6=location

x_move=as.vector(x_acc[94,])
z_move=as.vector(z_acc[94,])
y_move=as.vector(y_acc[94,])


total <- rbind(x_move,y_move,z_move)
total=t(total)
total=total[-1,]
total=as.data.frame(total)
names(total)=c('x_acc','y_acc','z_acc')

velocity_x=cumsum(total$x_acc)
velocity_y=cumsum(total$y_acc)
velocity_z=cumsum(total$z_acc)
velocity=data.frame(velocity_x,velocity_y,velocity_z)


location_x=cumsum(velocity_x)
location_y=cumsum(velocity_y)
location_z=cumsum(velocity_z)
location=data.frame(location_x,location_y,location_z)

location3=location

x_move=as.vector(x_acc[120,])
z_move=as.vector(z_acc[120,])
y_move=as.vector(y_acc[120,])


total <- rbind(x_move,y_move,z_move)
total=t(total)
total=total[-1,]
total=as.data.frame(total)
names(total)=c('x_acc','y_acc','z_acc')

velocity_x=cumsum(total$x_acc)
velocity_y=cumsum(total$y_acc)
velocity_z=cumsum(total$z_acc)
velocity=data.frame(velocity_x,velocity_y,velocity_z)


location_x=cumsum(velocity_x)
location_y=cumsum(velocity_y)
location_z=cumsum(velocity_z)
location=data.frame(location_x,location_y,location_z)

location4=location

x_move=as.vector(x_acc[96,])
z_move=as.vector(z_acc[96,])
y_move=as.vector(y_acc[96,])


total <- rbind(x_move,y_move,z_move)
total=t(total)
total=total[-1,]
total=as.data.frame(total)
names(total)=c('x_acc','y_acc','z_acc')

velocity_x=cumsum(total$x_acc)
velocity_y=cumsum(total$y_acc)
velocity_z=cumsum(total$z_acc)
velocity=data.frame(velocity_x,velocity_y,velocity_z)


location_x=cumsum(velocity_x)
location_y=cumsum(velocity_y)
location_z=cumsum(velocity_z)
location=data.frame(location_x,location_y,location_z)

location5=location

x_move=as.vector(x_acc[77,])
z_move=as.vector(z_acc[77,])
y_move=as.vector(y_acc[77,])


total <- rbind(x_move,y_move,z_move)
total=t(total)
total=total[-1,]
total=as.data.frame(total)
names(total)=c('x_acc','y_acc','z_acc')

velocity_x=cumsum(total$x_acc)
velocity_y=cumsum(total$y_acc)
velocity_z=cumsum(total$z_acc)
velocity=data.frame(velocity_x,velocity_y,velocity_z)


location_x=cumsum(velocity_x)
location_y=cumsum(velocity_y)
location_z=cumsum(velocity_z)
location=data.frame(location_x,location_y,location_z)

location1=location

x_move=as.vector(x_acc[101,])
z_move=as.vector(z_acc[101,])
y_move=as.vector(y_acc[101,])


total <- rbind(x_move,y_move,z_move)
total=t(total)
total=total[-1,]
total=as.data.frame(total)
names(total)=c('x_acc','y_acc','z_acc')

velocity_x=cumsum(total$x_acc)
velocity_y=cumsum(total$y_acc)
velocity_z=cumsum(total$z_acc)
velocity=data.frame(velocity_x,velocity_y,velocity_z)


location_x=cumsum(velocity_x)
location_y=cumsum(velocity_y)
location_z=cumsum(velocity_z)
location=data.frame(location_x,location_y,location_z)

location2=location

x_move=as.vector(x_acc[86,])
z_move=as.vector(z_acc[86,])
y_move=as.vector(y_acc[86,])


total <- rbind(x_move,y_move,z_move)
total=t(total)
total=total[-1,]
total=as.data.frame(total)
names(total)=c('x_acc','y_acc','z_acc')

velocity_x=cumsum(total$x_acc)
velocity_y=cumsum(total$y_acc)
velocity_z=cumsum(total$z_acc)
velocity=data.frame(velocity_x,velocity_y,velocity_z)


location_x=cumsum(velocity_x)
location_y=cumsum(velocity_y)
location_z=cumsum(velocity_z)
location=data.frame(location_x,location_y,location_z)

location7=location


setnames(x_acc,'X1','class')
x_acc$class=as.vector(x_acc$class)
x_acc=as.data.table(x_acc)
x_acc=x_acc[order(class)]
x_acc[,class:=as.character(class)]
x_acc[,id:=1:.N]
long_x=melt(x_acc,id.vars=c('id','class'))


long_x[,time:=as.numeric(gsub("\\D", "", variable))-1]

long_x=long_x[,list(id,class,time,value)]
long_x=long_x[order(id,time)]

ggplot(long_x, aes(time,value)) + geom_line(aes(color=as.character(id)),) +
  facet_wrap(~class)


selected_series=1
segment_length=10


long_x=long_x[order(id,time)]

data_ts=long_x[id==selected_series]$value
paa_rep=repr_paa(data_ts, segment_length, meanC)
plot(paa_rep,type='l')
paa_rep

data_plot=long_x[id==selected_series]
dummy_time=c(1:(length(paa_rep)))*segment_length 
dummy_time=c(dummy_time,nrow(data_plot))   








dt_paa=data.table(time=dummy_time,paa_rep=paa_rep)
head(dt_paa)

data_plot=merge(data_plot,dt_paa,by='time',all.x=T)
data_plot[,paa_rep:=nafill(paa_rep,'nocb')] 



data_plot=melt(data_plot,id.vars='time',
               measure.vars=c('value','paa_rep'))

ggplot(data_plot,aes(x=time,y=value,color=variable))+
  geom_line()

data_plot=merge(data_plot,long_x[id==selected_series,list(time,obs=value)],by='time')

head(data_plot)

data_plot[,list(sse=sum((value-obs)^2)),list(variable)]

data_plotpaa=data_plot

paavecin=data_plotpaa[,data_plotpaa$variable=='paa_rep']
paavector=data_plotpaa[paavecin]
paavector$obs=NULL
paavector



selected_dt=long_x[id==selected_series]

tree_fit=rpart(value~time,selected_dt,control=rpart.control(maxdepth=2))

fancyRpartPlot(tree_fit)

selected_dt[,tree_rep:=predict(tree_fit,selected_dt)]

data_plot=melt(selected_dt,id.vars='time',measure.vars=c('value','tree_rep'))

appended=rbind(data_plot,paavector)




```

## R Markdown



```{r cars}
x_acc <- read_table("D:/İndirilenler/uWaveGestureLibrary_X_TRAIN",col_names = FALSE)
y_acc <- read_table("D:/İndirilenler/uWaveGestureLibrary_Y_TRAIN",col_names = FALSE)
z_acc <- read_table("D:/İndirilenler/uWaveGestureLibrary_Z_TRAIN",col_names = FALSE)

x_move=as.vector(x_acc[92,])
z_move=as.vector(z_acc[92,])
y_move=as.vector(y_acc[92,])

total <- rbind(x_move,y_move,z_move)
total=t(total)
total=total[-1,]
total=as.data.frame(total)
names(total)=c('x_acc','y_acc','z_acc')




acceleration=as.ts(total)




velocity_x=cumsum(total$x_acc)
velocity_y=cumsum(total$y_acc)
velocity_z=cumsum(total$z_acc)

velocity=data.frame(velocity_x,velocity_y,velocity_z)
tsvelocity=as.ts(velocity)


location_x=cumsum(velocity_x)
location_y=cumsum(velocity_y)
location_z=cumsum(velocity_z)
location=data.frame(location_x,location_y,location_z)
tslocation=as.ts(location)

location8=location



```


## Including Plots



```{r pressure, echo=FALSE}

scatterplot3d(location1,type = "h",main="Instance from Class 1")
scatterplot3d(location2,type = "h",main="Instance from Class 2")
scatterplot3d(location3,type = "h",main="Instance from Class 3")
scatterplot3d(location4,type = "h",main="Instance from Class 4")
scatterplot3d(location5,type = "h",main="Instance from Class 5")
scatterplot3d(location6,type = "h",main="Instance from Class 6")
scatterplot3d(location7,type = "h",main="Instance from Class 7")
scatterplot3d(location8,type = "h",main="Instance from Class 8")

```

## R Markdown

As different classes show significant differences in their rotating axis (clockwise-counter clockwise), number of times origin axises are visited and distance from their starting point using tree approach is useful for most of the instances as it keeps the most of their "concentrated" data. The second approach for representation is "Piecewise Aggregate Approximation". It is not as concentrated as tree approach yet it uses only 10% of the data with loss of 10.08 sse point. 

```{r represent, echo=FALSE}


ggplot(appended,aes(x=time,y=value,color=variable))+
  geom_line()+ggtitle("Plot of Piecewise Aggregate Approximation Approach and Tree Approach")


```
